Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-08 mplr-2021/main.tex
Migrate progamming2021 to mplr-2021

% -*- coding: utf-8; -*-
\documentclass[english,cleveref,autoref,submission]{programming}
% Programming:
% The main part of the paper should not exceed 22 pages (in the
% provided style of the journal), but there is no limit for
% bibliography and appendices. The page limit for the main part of the
% paper is in place in order to keep the paper on focus and to avoid
% overloading the reviewers. Authors are encouraged to move important
% details to appendices, which may be consulted by the reviewers. In
% some cases, if authors feel that the main part requires
% substantially more pages, they should explain the reasons why in the
% additional comments field of the submission form; examples of these
% cases may include papers with substantial source code listings, and
% essays. Papers whose length is incommensurate with their
% contribution will be rejected.

\usepackage[backend=biber]{biblatex}
\addbibresource{main.bib}

@@

\newenvironment{changethis}{%
  \begin{tcolorbox}[breakable,notitle,boxrule=0pt,colback=blue!20,colframe=blue!20]}{%
  \end{tcolorbox}}

\input{macros}

\definecolor{backgroundgray}{rgb}{.94,.94,.94}
\definecolor{lightgray}{rgb}{.35,.35,.5}
\definecolor{darkgray}{rgb}{.2, .2, .2}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}

\newcommand{\secref}[1]{Section~\ref{#1} - \nameref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\coderef}[1]{Listing~\ref{#1}}

@@

%%\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Generation of TypeScript Declaration Files from JavaScript Code}
\subtitle{Catching the Developer's Intent from Examples}
% \titlerunning{Dummy short title}%optional, please use if title is longer than one line

\author{Fernando Cristiani}
\authorinfo{\email{fernando.cristiani@hs-karlsruhe.de}}
\affiliation{Hochschule Karlsruhe, Germany}

\author{Peter Thiemann}
\authorinfo{\email{thiemann@informatik.uni-freiburg.de}}
\affiliation{Albert-Ludwigs-Universität Freiburg, Germany}

\keywords{JavaScript, TypeScript, Dynamic Analysis, Declaration Files}%TODO mandatory; please add comma-separated list of 1--5 keywords

%%%%%%%%%%%%%%%%%%
%% These data MUST be filled for your submission. (see 5.3)
\paperdetails{
  %% perspective options are: art, sciencetheoretical, scienceempirical, engineering.
  %% Choose exactly the one that best describes this work. (see 2.1)
  perspective=science-empirical,
  %% State one or more areas, separated by a comma. (see 2.2)
  %% Please see list of areas in http://programming-journal.org/cfp/
  %% The list is open-ended, so use other areas if yours is/are not listed.
  area={General-purpose programming, Web programming},
  %% You may choose the license for your paper (see 3.)
  %% License options include: cc-by (default), cc-by-nc
  % license=cc-by,
}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
%% These data are provided by the editors. May be left out on submission.
%\paperdetails{
%  submitted=2016-08-10,
%  published=2016-10-11,
%  year=2016,
%  volume=1,
%  issue=1,
%  articlenumber=1,
%}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please go to https://dl.acm.org/ccs/ccs.cfm and generate your Classification
% System [view CCS TeX Code] stanz and copy _all of it_ to this place.
%% From HERE
%%% !!! REVISE
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002944.10011122.10003459</concept_id>
<concept_desc>General and reference~Computing standards, RFCs and guidelines</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010405.10010476.10010477</concept_id>
<concept_desc>Applied computing~Publishing</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Software and its engineering~Software notations and tools}
\ccsdesc[100]{Software and its engineering~General programming languages}

% To HERE
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

%TODO mandatory: add short abstract of the document
\begin{abstract}
Developers are starting to write large and complex applications in
TypeScript, a typed dialect of JavaScript. TypeScript applications
integrate JavaScript libraries via typed descriptions of their APIs
called declaration files. DefinitelyTyped is the standard public
repository for these files.
The repository is populated and maintained manually by volunteers, which
is error prone and time consuming. Discrepancies between a
declaration file and the JavaScript implementation lead to
incorrect feedback from the TypeScript IDE and thus to incorrect uses
of the underlying JavaScript library.

@@

@@

\begin{lstlisting}[
    caption={\textbf{Unintuitive JavaScript behavior:} Falsy values,
    \lstinline!null! vs. \lstinline!undefined!,
 \lstinline!typeof!, and type coercion},
    language=JavaScript,
	label=code:introduction-javascript-wtfs,
    float=bp,
    captionpos=b
]
"0" == false; // true
true == "1.00"; // true
false == "    \n\r\t     "; // true
false == []; // true
0 == []; // true
null == undefined; // true
null + undefined + [1, 2, 3] // 'NaN1,2,3' 
typeof null; // object
null instanceof Object; // false
[1] + 1; //'11'
[2] == "2"; // true
"hello world".lenth + 1 // NaN | note 'lenth' instead of 'length'
[1, 15, 20, 100].sort() // [ 1, 100, 15, 20 ]
\end{lstlisting}
% "01" < "00100"; // false 
% pjt: why unexpected?

@@

As an example, consider the NPM\footnote{NPM is the \href{https://www.npmjs.com/}{Node package
  manager}, an online repository for JavaScript modules.} module
\texttt{abs} that
``computes the absolute path of an input''. Its documentation consists
of the following three examples\footnote{\url{https://www.npmjs.com/package/abs}}.
\begin{lstlisting}[language=JavaScript,numbers=none]
const abs = require("abs");

@@

console.log(abs("~/foo"));
// => "/home/username/foo"
\end{lstlisting}
From the examples, our tool generates a TypeScript declaration file,
which is equivalent to the declaration file provided in
DefinitelyTyped\footnote{\url{https://github.com/DefinitelyTyped/DefinitelyTyped/blob/master/types/abs/index.d.ts}}: 
\begin{lstlisting}[language=TypeScript,numbers=none]
export = Abs;
declare function Abs(input: string): string;
\end{lstlisting}
% \begin{description}
% \item[PJT: maybe later] Some previous work tackled the problem of improving
%   the quality of declaration files. Feldthaus et al
%   \cite{DBLP:conf/oopsla/FeldthausM14} search automatically for
%   mismatches between a declaration file and implementation
%   code. TSTest \cite{DBLP:journals/pacmpl/KristensenM17} adapted
%   feedback-directed random testing to detect discrepancies between a
%   declaration file and a JavaScript library. Tools like TSInfer and
%   TSEvolve~\cite{DBLP:conf/fase/KristensenM17} are designed for
%   assisting the creation of new declaration files and supporting the
%   evolution the declaration file when the corresponding JavaScript
%   library gets modified, respectively. They rely on an existing static
%   analyzer for JavaScript \cite{DBLP:conf/sas/JensenMT09}.  TypeScript
%   itself developed \texttt{dts-gen}, a tool that generates a
%   declaration file that is meant to be used as a \emph{starting point
%     for writing a high-quality declaration file} \cite{dts-gen}.
% \end{description}

@@

}
    \end{lstlisting}
  % \end{subfigure}
  \begin{center}
    \includegraphics[width=0.8\linewidth]{motivating-example-glob-to-regexp-vscode.png}
  \end{center}

  \caption{\textbf{Declaration file for \texttt{glob-to-regexp}
      generated with \texttt{dts-generate}} - The interface is
    detected correctly. Optional parameters are detected. The
    declaration file is usable in Visual Studio
    Code\footnote{https://code.visualstudio.com}.} 
  \label{fig:motivating-example-glob-to-regexp-vscode}
\end{figure}

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=1\linewidth]{dts-generate-block-diagram.pdf}
    \caption[dts-generate - Architecture overview]{\textbf{dts-generate - Architecture
        overview} - The initial code base is retrieved from the \NPM{} package's
      repository.
      Run-time information is gathered driven by example code.
      A TypeScript Declaration File is generated using run-time
      information.
      % A Symbolic Execution Engine creates test cases based on the generated
      % Declaration File and via a feedback loop enriches the code base until the stopping
      % criteria is reached.
      % The final TypeScript Declaration File gets returned.
      % Feedback
      % loop through the Symbolic Execution Engine was not implemented. It can be added in a
      % future to the existing architecture, without modifying the working blocks.
    } 
    \label{fig:tsd_generation_method_block_diagram}
  \end{figure}

@@

\begin{table}[tp]
  \begin{center}
    \begin{tabular}{ |l|c|r| } 
      \hline
      \textbf{TypeScript feature} & \textbf{Count} & \multicolumn{1}{|c|}{\textbf{\%}} \\ 
      \hline
      type-string & 5086 & 76.50\% \\
      optional-parameter & 4915 & 73.93\% \\
      type-boolean & 3891 & 58.53\% \\
      type-number & 3699 & 55.64\% \\
      type-void & 3548 & 53.37\% \\
      type-union & 3456 & 51.99\% \\
      type-function & 3286 & 49.43\% \\
      type-array & 3264 & 49.10\% \\
      type-any & 3127 & 47.04\% \\
      type-literals & 1925 & 28.96\% \\
      alias-type & 1899 & 28.56\% \\
      index-signature & 1271 & 19.12\% \\
      generics-function & 1145 & 17.22\% \\
      dot-dot-dot-token & 882 & 13.27\% \\
      call-signature & 817 & 12.29\% \\
      generics-interface & 718 & 10.80\% \\
      type-object & 661 & 9.94\% \\
      type-undefined & 577 & 8.68\% \\
      type-intersection & 431 & 6.48\% \\
      readonly & 373 & 5.61\% \\
      type-tuple & 355 & 5.34\% \\
      generics-class & 265 & 3.99\% \\
      static & 251 & 3.78\% \\
      private & 82 & 1.23\% \\
      public & 43 & 0.65\% \\
      protected & 19 & 0.29\% \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Distribution of TypeScript features in declaration files uploaded to DefinitelyTyped (DT). The 2nd column shows how many files in DT make use of a specific TypeScript feature. The 3rd column shows the corresponding percentage for a total of 6648 declaration files in DT. Numbers were obtained from commit \texttt{da93d7b13094bacb170ead3f4a289f3b8687e4e5} (April 4, 2020).}
  \label{tab:dts-parse-stats}
\end{table}

% \paragraph*{Interfaces}
Finally, interfaces are created by exploring \texttt{getField} and \texttt{methodCall} interactions from the run-time information. We
gather the interactions for a specific argument and build the
interface by incrementally adding new properties. Interactions within
the \texttt{followingInteractions} field are recursively traversed,
building a new interface at each level up to a predefined depth. Interfaces that turn out
to be equivalent are merged.

@@

\begin{figure}[tp]
    \begin{centering}
        {\includegraphics[width=1\textwidth]{evaluation-diagram.pdf}}
        \caption[Evaluation against DefinitelyTyped Repository]{\textbf{Evaluation of
            generated declaration files against DefinitelyTyped Repository} - The parser
          uses the TypeScript Compiler           API \cite{typescript-compiler-api} to
          transform declaration files into an abstract syntax which is serialized in
          JSON. The comparison is performed on the JSON format.} 
        \label{fig:evaluation-diagram}
    \end{centering}
\end{figure}

@@

\definecolor{myellow}{RGB}{228,212,0}
\definecolor{mgreen}{RGB}{5,104,57}

\newcommand\funnel[3]{%
\pgfmathsetmacro\mwid{(0.3+\val*0.06)}
\pgfmathsetmacro\mradius{(\val*0.01 + 1)}
\pgfmathsetmacro\mheight{(\val*0.003 + 0.4)}
\pgfmathsetmacro\marc{\mwid-.4}
    \begin{scope}[%
        shift={(0,#1)}, 
        line width=.05pt, 
        %x=5mm, 
        scale=0.7,
        yshift=\xi*0.05
        ]
    \draw[black,bottom color=#2, top color=#2] (-\mwid,0) -- (-\mwid+.4,-\mheight) arc (190:350:\marc cm and \mradius mm) -- (\mwid,0);
    \draw[black,fill=#3] (0,0) ellipse (\mwid cm and \mradius mm);
    \path (-\mwid,0) -- (-\mwid+.4,-\mheight) coordinate[midway] (a\xi);
    \end{scope}
}

\begin{figure}[tp]
	\hspace*{-0.16\textwidth}
	\centering
	\begin{tikzpicture}
		\foreach \val
				[%
				count=\xi starting from 0, 
				evaluate=\xi as \shadecolor using int(25*\xi),
				evaluate=\xi as \coord using int(\xi-12)
				]
			in {
				4.05,
				7.33,
				18.02,
				37.49,
				71.19,
				82.50,
				100.00
			}{
				\funnel{\coord}{mgreen!\shadecolor !myellow}{mgreen!\shadecolor !myellow}
			}

		\node[left=0.02\textwidth of a0] {Generated Declaration Files};
		\node[right=0.04\textwidth of a0] {\textbf{244}};

		\node[left=0.02\textwidth of a1] {Run-time Information};
		\node[right=0.06\textwidth of a1] {\textbf{436}};

		\node[left=0.02\textwidth of a2] {Working Examples};
		\node[right=0.17\textwidth of a2] {\textbf{946}};

		\node[left=0.02\textwidth of a3] {Code Examples};
		\node[right=0.25\textwidth of a3] {\textbf{2260}};

		\node[left=0.02\textwidth of a4] {README file};
		\node[right=0.45\textwidth of a4] {\textbf{4292}};

		\node[left=0.02\textwidth of a5] {Github Repository};
		\node[right=0.52\textwidth of a5] {\textbf{4974}};

		\node[align=right,left=0.02\textwidth of a6, text width=0.25\textwidth] {Definitely Typed Modules};
		\node[right=0.62\textwidth of a6] {\textbf{6029}};

	\end{tikzpicture}
	\caption[Number of analyzed modules for each stage of the experiment]{\textbf{Number of analyzed modules for each stage of the experiment} - A TypeScript Declaration File was generated for only 244 modules, out of 6029 modules in the DefinitelyTyped Repository. It was possible to gather valid run-time information for only 25\% of the modules for which a Code Example was extracted.}
	\label{fig:experiments-overall-funnel}
\end{figure}

@@

\subsection{Declaration Files Generation}
\label{sec:experiments-declaration-files-generation}

%%% !!! TBC !!!

@@

\printbibliography
%%\bibliography{main}

\end{document}

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.

\input{macros}
\newcommand{\secref}[1]{Section~\ref{#1} - \nameref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\coderef}[1]{Listing~\ref{#1}}

\documentclass[sigconf]{acmart}
\usepackage{listings}

@@

\usepackage{subcaption}

\usepackage[htt]{hyphenat}

\definecolor{backgroundgray}{rgb}{.94,.94,.94}

@@

\settopmatter{printfolios=true}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Generation of TypeScript Declaration Files from JavaScript Code}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Fernando Cristiani}
\affiliation{%
  \institution{Hochschule Karlsruhe}
  \city{Karlsruhe}
  \country{Germany}}
\email{fernando.cristiani@hs-karlsruhe.de}

\author{Peter Thiemann}
\affiliation{%
  \institution{Albert-Ludwigs-Universit{\"a}t Freiburg}
  \city{Freiburg}
  \country{Germany}
}
\email{thiemann@informatik.uni-freiburg.de}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Developers are starting to write large and complex applications in
  TypeScript, a typed dialect of JavaScript. TypeScript applications
  integrate JavaScript libraries via typed descriptions of their APIs
  called declaration files. DefinitelyTyped is the standard public
  repository for these files.
  The repository is populated and maintained manually by volunteers, which
  is error prone and time consuming. Discrepancies between a
  declaration file and the JavaScript implementation lead to
  incorrect feedback from the TypeScript IDE and thus to incorrect uses
  of the underlying JavaScript library.

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{JavaScript, TypeScript, Dynamic Analysis, Declaration Files}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
% \begin{teaserfigure}
%   GRAPHICS REMOVED % \includegraphics[width=\textwidth]{sampleteaser}
%   \caption{Seattle Mariners at Spring Training, 2010.}
%   \Description{Enjoying the baseball game from the third-base
%   seats. Ichiro Suzuki preparing to bat.}
%   \label{fig:teaser}
% \end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

\begin{lstlisting}[
  caption={\textbf{Unintuitive JavaScript behavior:} Falsy values,
  \lstinline!null! vs. \lstinline!undefined!,
\lstinline!typeof!, and type coercion},
  language=JavaScript,
label=code:introduction-javascript-wtfs,
  float=bp,
  captionpos=b
]
"0" == false; // true
true == "1.00"; // true
false == "    \n\r\t     "; // true
false == []; // true
0 == []; // true
null == undefined; // true
null + undefined + [1, 2, 3] // 'NaN1,2,3' 
typeof null; // object
null instanceof Object; // false
[1] + 1; //'11'
[2] == "2"; // true
"hello world".lenth + 1 // NaN | note 'lenth' instead of 'length'
[1, 15, 20, 100].sort() // [ 1, 100, 15, 20 ]
\end{lstlisting}

@@

As an example, consider the NPM\footnote{NPM is the \href{https://www.npmjs.com/}{Node package
  manager}, an online repository for JavaScript modules.} module
\texttt{abs} that
``computes the absolute path of an input''. Its documentation consists
of the following three examples\footnote{\url{https://www.npmjs.com/package/abs}}.

\begin{lstlisting}[language=JavaScript,numbers=none]
const abs = require("abs");

@@

console.log(abs("~/foo"));
// => "/home/username/foo"
\end{lstlisting}
From the examples, our tool generates a TypeScript declaration file,
which is equivalent to the declaration file provided in
DefinitelyTyped\footnote{\url{https://github.com/DefinitelyTyped/DefinitelyTyped/blob/master/types/abs/index.d.ts}}:

\begin{lstlisting}[language=TypeScript,numbers=none]
export = Abs;
declare function Abs(input: string): string;
\end{lstlisting}

% \begin{description}
% \item[PJT: maybe later] Some previous work tackled the problem of improving
%   the quality of declaration files. Feldthaus et al
%   \cite{DBLP:conf/oopsla/FeldthausM14} search automatically for
%   mismatches between a declaration file and implementation
%   code. TSTest \cite{DBLP:journals/pacmpl/KristensenM17} adapted
%   feedback-directed random testing to detect discrepancies between a
%   declaration file and a JavaScript library. Tools like TSInfer and
%   TSEvolve~\cite{DBLP:conf/fase/KristensenM17} are designed for
%   assisting the creation of new declaration files and supporting the
%   evolution the declaration file when the corresponding JavaScript
%   library gets modified, respectively. They rely on an existing static
%   analyzer for JavaScript \cite{DBLP:conf/sas/JensenMT09}.  TypeScript
%   itself developed \texttt{dts-gen}, a tool that generates a
%   declaration file that is meant to be used as a \emph{starting point
%     for writing a high-quality declaration file} \cite{dts-gen}.
% \end{description}

@@

}
    \end{lstlisting}
  % \end{subfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{motivating-example-glob-to-regexp-vscode.png}
  \end{center}

  \caption{Declaration file for \texttt{glob-to-regexp} 
    generated with \texttt{dts-generate} - The interface is
    detected correctly. Optional parameters are detected. The declaration 
    file is usable in Visual Studio Code\protect\footnote{\url{https://code.visualstudio.com}}} 
  \label{fig:motivating-example-glob-to-regexp-vscode}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\linewidth]{dts-generate-block-diagram.pdf}
  \caption[dts-generate - Architecture overview]{dts-generate - Architecture
      overview - The initial code base is retrieved from the \NPM{} package's
    repository.
    Run-time information is gathered driven by example code.
    A TypeScript Declaration File is generated using run-time
    information.
    % A Symbolic Execution Engine creates test cases based on the generated
    % Declaration File and via a feedback loop enriches the code base until the stopping
    % criteria is reached.
    % The final TypeScript Declaration File gets returned.
    % Feedback
    % loop through the Symbolic Execution Engine was not implemented. It can be added in a
    % future to the existing architecture, without modifying the working blocks.
  } 
  \label{fig:tsd_generation_method_block_diagram}
\end{figure}

@@

\begin{table}[tp]
  \caption{Distribution of TypeScript features in declaration files uploaded to DefinitelyTyped (DT). The 2nd column shows how many files in DT make use of a specific TypeScript feature. The 3rd column shows the corresponding percentage for a total of 6648 declaration files in DT. Numbers were obtained from commit \texttt{da93d7b13094bacb170ead3f4a289f3b8687e4e5} (April 4, 2020).}
  \begin{center}
    \begin{tabular}{ |l|c|r| } 
      \hline
      \textbf{TypeScript feature} & \textbf{Count} & \multicolumn{1}{|c|}{\textbf{\%}} \\ 
      \hline
      type-string & 5086 & 76.50\% \\
      optional-parameter & 4915 & 73.93\% \\
      type-boolean & 3891 & 58.53\% \\
      type-number & 3699 & 55.64\% \\
      type-void & 3548 & 53.37\% \\
      type-union & 3456 & 51.99\% \\
      type-function & 3286 & 49.43\% \\
      type-array & 3264 & 49.10\% \\
      type-any & 3127 & 47.04\% \\
      type-literals & 1925 & 28.96\% \\
      alias-type & 1899 & 28.56\% \\
      index-signature & 1271 & 19.12\% \\
      generics-function & 1145 & 17.22\% \\
      dot-dot-dot-token & 882 & 13.27\% \\
      call-signature & 817 & 12.29\% \\
      generics-interface & 718 & 10.80\% \\
      type-object & 661 & 9.94\% \\
      type-undefined & 577 & 8.68\% \\
      type-intersection & 431 & 6.48\% \\
      readonly & 373 & 5.61\% \\
      type-tuple & 355 & 5.34\% \\
      generics-class & 265 & 3.99\% \\
      static & 251 & 3.78\% \\
      private & 82 & 1.23\% \\
      public & 43 & 0.65\% \\
      protected & 19 & 0.29\% \\
      \hline
    \end{tabular}
  \end{center}
  \label{tab:dts-parse-stats}
\end{table}

Finally, interfaces are created by exploring \texttt{getField} and \texttt{methodCall} interactions from the run-time information. We
gather the interactions for a specific argument and build the
interface by incrementally adding new properties. Interactions within
the \texttt{followingInteractions} field are recursively traversed,
building a new interface at each level up to a predefined depth. Interfaces that turn out
to be equivalent are merged.

@@

\begin{figure}[tp]
  \begin{centering}
      {\includegraphics[width=1\linewidth]{evaluation-diagram.pdf}}
      \caption[Evaluation against DefinitelyTyped Repository]{\textbf{Evaluation of
          generated declaration files against DefinitelyTyped Repository} - The parser
        uses the TypeScript Compiler           API \cite{typescript-compiler-api} to
        transform declaration files into an abstract syntax which is serialized in
        JSON. The comparison is performed on the JSON format.} 
      \label{fig:evaluation-diagram}
  \end{centering}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\linewidth]{funnel.png}
  \caption[Number of analyzed modules for each stage of the experiment]{
    \textbf{Number of analyzed modules for each stage of the experiment} - 
  A TypeScript Declaration File was generated for only 244 modules, out of 6029 modules in the DefinitelyTyped Repository. 
  It was possible to gather valid run-time information for only 25\% of the modules for which a Code Example was extracted.
  } 
  \label{fig:experiments-overall-funnel}
\end{figure}

@@

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{main}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.
